Binning Strategies and Related Loss for Large Data

### 2014-10-19 Paper.Rnw
update to new dbData package and new database on mysql2

connect <- dbConnect(dbDriver("MySQL"), user="2009Expo", 
                   password="R R0cks", port=3306, dbname="baseball", 
                   host="headnode.stat.iastate.edu")
pitch <- new("dataDB", co=connect, table="Pitching")

@@

  res <- data.frame(sapply(1:(k-1), function(var) {
			return(rep(x[,var], x[,k]))
		}
	))
	names(res) <- names(x)[1:(k-1)]
	return(res)
}
d1.ext <- xtd.data(d1)
@
<<scatterplots, echo=F,include=F>>=
qplot(data=d1.ext, x=G, y=SO, geom="point", main="Games and Strike Outs in ML Baseball", alpha=I(.05), size=I(3)) + theme_bw() + xlab("Games (Count)")+ ylab("Strike Outs (Count)")
  ggsave("./figure/OverplottingAlpha.pdf", width=5, height=5)
qplot(data=d1, x=G, y=SO, geom="point", main="Games and Strike Outs in ML Baseball", size=I(3)) + theme_bw() + xlab("Games (Count)")+ ylab("Strike Outs (Count)")
  ggsave("./figure/Overplotting.pdf", width=5, height=5)
qplot(data=d1, x=G, y=SO, geom="point", main="Games and Strike Outs in ML Baseball", shape="o", size=I(6)) + scale_shape_identity() + theme_bw() + xlab("Games (Count)")+ ylab("Strike Outs (Count)")
  ggsave("./figure/OverplottingCircles.pdf", width=5, height=5)
qplot(data=d1.ext, x=G, y=SO, geom="hex", fill=..count.., group=1) +  
  scale_fill_gradient("Frequency", low="#56B1F7", high="#132B43", guide="legend", trans="log", breaks=c(1, 10, 100, 1000)) + theme_bw() + xlab("Games (Count)") + ylab("Strike Outs (Count)") + theme(legend.position="bottom")
  ggsave("./figure/HexBinning.pdf", width=5, height=5)
d1.hex.obj <- hexbin(d1.ext$G, d1.ext$SO)
d1.hex <- data.frame(hcell2xy(d1.hex.obj))
names(d1.hex) <- c("G", "SO")
d1.hex$Freq <-  d1.hex.obj@count
qplot(data=d1.hex, x=G, y=SO, geom="point", size=Freq) + 
  scale_area("Frequency", range=c(1, 4), trans="log", breaks=c(1, 10, 100, 1000, 10000))+ theme_bw() + xlab("Games (Count)")+ ylab("Strike Outs (Count)") + theme(legend.position="bottom")
  ggsave("./figure/BinScatter.pdf", width=5, height=5)

>>>>

connect <- dbConnect(dbDriver("MySQL"), host="mysql2.stat.iastate.edu", 
                     port=3306, user="dbaccess", dbname="baseball")
pitch <- new("dataDB", co=connect, table="Pitching")

@@

  res <- data.frame(sapply(1:(k-1), function(var) {
			return(rep(x[,var], x[,k]))
		}
	))
	names(res) <- names(x)[1:(k-1)]
	return(res)
}
d1.ext <- xtd.data(d1)
@
<<scatterplots, echo=F,include=F>>=
qplot(data=d1.ext, x=G, y=SO, geom="point", main="Games and Strike Outs in ML Baseball", alpha=I(.05), size=I(3)) + theme_bw() + xlab("Games (Count)")+ ylab("Strike Outs (Count)")
  ggsave("./figure/OverplottingAlpha.pdf", width=5, height=5)
qplot(data=d1, x=G, y=SO, geom="point", main="Games and Strike Outs in ML Baseball", size=I(3)) + theme_bw() + xlab("Games (Count)")+ ylab("Strike Outs (Count)")
  ggsave("./figure/Overplotting.pdf", width=5, height=5)
qplot(data=d1, x=G, y=SO, geom="point", main="Games and Strike Outs in ML Baseball", shape="o", size=I(6)) + scale_shape_identity() + theme_bw() + xlab("Games (Count)")+ ylab("Strike Outs (Count)")
  ggsave("./figure/OverplottingCircles.pdf", width=5, height=5)
qplot(data=d1.ext, x=G, y=SO, geom="hex", fill=..count.., group=1) +  
  scale_fill_gradient("Frequency", low="#56B1F7", high="#132B43", guide="legend", trans="log", breaks=c(1, 10, 100, 1000)) + theme_bw() + xlab("Games (Count)") + ylab("Strike Outs (Count)") + theme(legend.position="bottom")
  ggsave("./figure/HexBinning.pdf", width=5, height=5)
d1.hex.obj <- hexbin(d1.ext$G, d1.ext$SO)
d1.hex <- data.frame(hcell2xy(d1.hex.obj))
names(d1.hex) <- c("G", "SO")
d1.hex$Freq <-  d1.hex.obj@count
qplot(data=d1.hex, x=G, y=SO, geom="point", size=Freq+1) + 
  scale_size_area("Frequency", max_size=4, trans="log", breaks=c(1, 10, 100, 1000, 10000))+ theme_bw() + xlab("Games (Count)")+ ylab("Strike Outs (Count)") + theme(legend.position="bottom")
  ggsave("./figure/BinScatter.pdf", width=5, height=5)
